drivers response diversity

### 2024-07-08 drivers_response_diversity.Rmd
new plots 3 and 4

##Drivers of thermal response diversity

@@

###Species richness and eutrophication
Multiple linear regression to calculate the effect of species richness and
eutrophication on response diversity.

###Fig. 3

@@

@@

# Lms for all categories: endemic, translcated, non_native and non_endemic_native
# with data on all lakes
# Endemic
lm_endemic <- lm(mean_rdiv ~ endemic, data = df_lm)

@@

plot_all_lms
# save as TIFF
# tiff(paste("total_models/plots/lm_all.tiff", sep = ""), units="in", width=11, height=7, res=300)
# # plot(ggarrange(depth1, depth2, ncol = 2))
# # plot science discussion
# plot(plot_all_lms)
# 
# dev.off()

@@

###Figure 4
```{r}
```

###Figure 3 Divergence

@@

```{r}
# second lm for maximum phosphorus ~ species richness
lm2 <- lm(mean_rdiv ~ Phos_max + sum_species, data = df_lm_excl)

@@

# Plot Fig. 3
"#78BE63"
mycolor <- c("color" = "#78BE63")
# mycolor <- c("color" = "#A0E66A")
"98D47C"

lm1_plot <- bind_model1 |> 
  ggplot(aes(sum_species, fit,  color = category, fill = category)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)),  alpha = 0.3, color = NA) +
  theme_classic(base_size = 20) +
  ylab("Mean dissimilarity") +
  xlab("Species richness") +
  # ylim(1,3) +
  scale_fill_manual(values = mycolor, aesthetics = c("color", "fill"), guide = NULL)

@@

# combine both plots
figure_3 <- ggarrange(lm1_plot, lm2_plot)

figure_3
# save as TIFF
# tiff(paste("total_models/plots/lm_species_richness_eutroph.tiff", sep = ""), units="in", width=12, height=5, res=300)
# 
# plot(figure_3)
# 
# # Closing the graphical device
# dev.off()

@@

###Divergence figure 4

@@

```
###Community subgroups
####Fig. 4a
We fitted simple linear models for the number of species in each category and the mean dissimilarity in each lake. 
```{r}
# Lms for all categories: endemic, translcated, non_native and non_endemic_native
# with data on all lakes
# Endemic
lm_endemic <- lm(mean_rdiv ~ endemic, data = df_lm)

>>>>

#Drivers of thermal response diversity

@@

##Fig. 3
Dissimilarity, species richness and categories

@@

mycolor = "black"

@@

lm1_plot
# Lms for all categories: endemic, translcated, non_native and non_endemic_native
# with data on all lakes
# Endemic
lm_endemic <- lm(mean_rdiv ~ endemic, data = df_lm)

@@

plot_all_lms <- df_all_lms|> 
  ggplot(aes(species_richness, fit, color = category, fill = category, linetype = category)) +  
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)), color = NA, alpha = 0.3) +
  theme_classic(base_size = 16) +
  ylab("Mean dissimilarity") +
  xlab("Species richness") +
  scale_fill_manual(values = mycolors,
                    aesthetics = c("color", "fill"),
                    labels = c("endemic", "non-native", "non-endemic native", "translocated")) +
   scale_linetype_manual(values = c("endemic" = "solid",
                                   "non_native" = "dashed",
                                   "non_endemic_native" = "solid",
                                   "translocated" = "dashed"), labels = c("endemic", "non-native", "non-endemic native", "translocated"))

plot_all_lms

# save as TIFF
# tiff(paste("total_models/plots/lm_all.tiff", sep = ""), units="in", width=11, height=7, res=300)
# # plot(ggarrange(depth1, depth2, ncol = 2))
# # plot science discussion
# plot(plot_all_lms)
# 
# dev.off()

@@

## Figure 3 Divergence

@@

## Figure 4
```{r}
# second lm for maximum phosphorus ~ species richness
lm2 <- lm(mean_rdiv ~ Phos_max + sum_species, data = df_lm_excl)

@@

# Plot Fig. 3
"#78BE63"
mycolor <- c("color" = "black")
# mycolor <- c("color" = "#A0E66A")
"98D47C"

@@

lm2_plot
# save as TIFF
# tiff(paste("total_models/plots/lm_species_richness_eutroph.tiff", sep = ""), units="in", width=12, height=5, res=300)
# 
# plot(figure_3)
# 
# # Closing the graphical device
# dev.off()

@@

## Figure 4 Divergence

@@

```
### OLD CODE Community subgroups
####Fig. 4a
We fitted simple linear models for the number of species in each category and the mean dissimilarity in each lake. 
```{r}
# Lms for all categories: endemic, translcated, non_native and non_endemic_native
# with data on all lakes
# Endemic
lm_endemic <- lm(mean_rdiv ~ endemic, data = df_lm)
